Corridor Project Proposal

### 2024-03-04 corridor_docs/masters_cmtee_proposal/eec_ms_proposal.Rmd
method citations added

We propose to conduct the field component of our study in seven of the Savannah River Site's experimental landscapes (i.e., 'blocks') designed to assess the ecological effects of corridors. Each experimental landscape (i.e., "block") consists of a 1-ha square central patch surrounded by four peripheral patches. All peripheral patches separated from the 150 m from the central patch and have the same area (~1.4 ha), However, the four peripheral patches differ in their level of connectivity to the central patch and edge:area ratio (Figure 1). 
<!-- The "connected patch" is 100m $\times$ 100m and connected to the center patch by a 150m $\times$ 25m corridor. The two "winged patches" are 100m $\times$ 100m; each of these patches has two linear projections of 75m $\times$ 25m extending from opposite sides of the patch. Finally, the "rectangular patch" is a 100m $\times$ 100m square to which an area equal to that of the corridor/wings has been attached to the edge furthest from the central patch  .  -->

@@

**_Field Methods - Dung removal_:** We will compare the efficacy of dung removal by beetle communities in connected, unconnected, and winged patches with a field experiment to be conducted in seven of the experimental blocks. We first will establish a grid of N = 4 points in each of the patches in which we previously sampled beetle diversity to test Prediction 1 (Figure 2). At each point in the grid we will place two 'plant saucers' filled with 3 inches of homogenized local soil in which we place 300 g of cow dung; one of the saucers will be protected with mesh to prevent beetle access. After 48 hours the saucers will be removed and the remaining dung will be weighed (the weight of the protected dung is used to correct for weight loss from desiccation). Experiments will be conducted monthly in each landscape (N = 6) months to capture temporal variation in patterns of dung removal. This field experiment will be complemented by a mesocosm study with experimentally assembled communities (based on the results of surveys for testing Prediction 1) to be conducted at the University of Florida.

>>>>

We propose to conduct the field component of our study in seven of the Savannah River Site's experimental landscapes (i.e., 'blocks') designed to assess the ecological effects of corridors[@tewksbury_corridors_2002]. Each experimental landscape (i.e., "block") consists of a 1-ha square central patch surrounded by four peripheral patches. All peripheral patches separated from the 150 m from the central patch and have the same area (~1.4 ha), However, the four peripheral patches differ in their level of connectivity to the central patch and edge:area ratio (Figure 1). 
<!-- The "connected patch" is 100m $\times$ 100m and connected to the center patch by a 150m $\times$ 25m corridor. The two "winged patches" are 100m $\times$ 100m; each of these patches has two linear projections of 75m $\times$ 25m extending from opposite sides of the patch. Finally, the "rectangular patch" is a 100m $\times$ 100m square to which an area equal to that of the corridor/wings has been attached to the edge furthest from the central patch  .  -->

@@

**_Field Methods - Dung removal_:** We will compare the efficacy of dung removal by beetle communities in connected, unconnected, and winged patches with a field experiment to be conducted in seven of the experimental blocks. We first will establish a grid of N = 4 points in each of the patches in which we previously sampled beetle diversity to test Prediction 1 (Figure 2). At each point in the grid we will place two 'plant saucers' filled with 3 inches of homogenized local soil in which we place 300 g of cow dung; one of the saucers will be protected with mesh to prevent beetle access. After 48 hours the saucers will be removed and the remaining dung will be weighed (the weight of the protected dung is used to correct for weight loss from desiccation)[@noriega_dung_2023]. Experiments will be conducted monthly in each landscape (N = 6) months to capture temporal variation in patterns of dung removal. This field experiment will be complemented by a mesocosm study with experimentally assembled communities (based on the results of surveys for testing Prediction 1) to be conducted at the University of Florida[@WOS:000311855000018].
